---
title: "BA-DA Dashboard"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    vertical_layout: fill
    social: [ "twitter", "facebook", "menu"]
    source_code: embed
---


```{r setup, include=FALSE}
# shortcut for inserting an r chunk -- Ctrl+Alt+i
# include=FALSE: this whole code chunk is excluded in the output 
library(flexdashboard)
library(knitr)
library(DT)
library(ggplot2)
library(dplyr)
```


```{r}
# data <- read.csv(file.choose()) 
# import datasets
# In this quick example, we don't import any dataset. Instead, we are using 'mpg' dataset from ggplot2 package
```

Key Descriptive Statistics
==============================
---
Note: ==== to indicate that this is a title for a dashboard page
---

Row
-------------------------------------

---
Note: ----- to indicate that it's going to be a row
---

### Scatter Plot of displ & hwy in mpg

```{r}
ggplot(mpg, aes(x = displ, y = hwy, color = factor(class))) +
  geom_point() +
  scale_color_brewer(palette = "Set3")
```

### Scatter Plot With a Smooth Line

```{r}
# color aesthetic specified for only the geom_point layer
ggplot(mpg, aes(x = displ, y = hwy)) +
  geom_point(aes(color = class)) +
  geom_smooth(se = FALSE) 
```

### Scatter Plot With Labels & Annotations

```{r}
## adding labels & annotations
ggplot(mpg, aes(x = displ, y = hwy)) +
  geom_point(aes(color = class)) +
  geom_smooth(se = FALSE) +
  labs(title = "Fuel Efficiency by Engine Power",
       subtitle = "Fuel economy data from 1999 and 2008 for 38 popular models of cars",
       x = "Engine power (litres displacement)",
       y = "Fuel Efficiency (miles per gallon)",
       color = "Car Type")

```


### Scatter Plot with Facets by year and cyl

```{r}
# faceting data by more than one categorical variable. 
ggplot(mpg, aes(x = displ, y = hwy)) +
  geom_point() +
  facet_grid(year ~ cyl)
```

Row
------------------------------------
### Bar Chart of class in mpg

```{r}
ggplot(data = mpg, aes(x = class)) +
  geom_bar(fill="dodgerblue", colour="grey40", alpha = .5)
```

### Bar Chart of class colored by drive (position = 'stack')

```{r}
# bar chart of class, colored by drive (front, rear, 4-wheel)
ggplot(mpg, aes(x = class, fill = drv)) + 
  geom_bar()
```

### Bar Chart of class colored by drive (position = 'dodge')

```{r}
# Alternatively, position = "dodge": values next to each other
ggplot(mpg, aes(x = class, fill = drv)) + 
  geom_bar(position = "dodge")
```

### Bar Chart of class colored by drive (x and y axis flipped)

```{r}
# flip x an y axis with coord flip
ggplot(mpg, aes(x = class, fill = drv)) + 
  geom_bar(position = "dodge") +
  coord_flip() # [inserted into the dashboard]
```

Row
------------------------------------
### Histogram of hwy in mpg

```{r}
# adding mean line 
ggplot(data = mpg, aes(x = hwy)) +
  geom_histogram(binwidth = 1.5, color = "grey30", fill = "white") +
  geom_vline(xintercept = mean(mpg$hwy), color = "red", linetype = "dashed", size = 1)
```

### Histogram of hwy in mpg colored by drv 
```{r}
## comparing groups using fill
# overlaying histograms
ggplot(data = mpg, aes(x = hwy, fill = drv)) +
  geom_histogram(binwidth = 1.5, alpha = .5) 
```

### Histogram of hwy in mpg faceted by drv and cyl

```{r}
## comparing groups using faceting by drv and cyl
ggplot(data = mpg, aes(x = hwy)) +
  geom_histogram(binwidth = 1.5, color = "grey30", fill = "white") +
  facet_grid(factor(drv) ~ factor(cyl))
```


### Overlap Histogram & Density Plot

```{r}
ggplot(data = mpg, aes(x = hwy)) +
  geom_histogram(aes(y = ..density..), binwidth = 1.5, color = "grey30", fill = "white") + 
  geom_density(alpha = .2, fill = "red")
```

Data Table
========================================

```{r}
datatable(mpg,
          caption = "Fuel economy data from 1999 to 2008 for 38 popular
                           models of cars",
          rownames = T,
          filter = "top",
          options = list(pageLength = 25))
```


Summary {data-orientation=columns} 
===========================================

Column 
-----------------------------------
### Max Highway Miles per Gallon (hwy)

```{r}
valueBox(max(mpg$hwy),
         icon = "fa-user" )
```

### Max City Miles per Gallon (cty)

```{r}
valueBox(max(mpg$cty),
         icon = "fa-user" )
```

### Average Highway Miles Per Gallon
```{r}
valueBox(round(mean(mpg$hwy),
               digits = 2),
         icon = "fa-area-chart")
```

### Average City Miles Per Gallon

```{r}
valueBox(round(mean(mpg$cty), digits = 2),
         icon = "fa-area-chart")
```

Column
---------------------------

Report

* This is a report on Fuel economy of popular models of `r length(mpg$model)` cars.

* The average city mpg is `r mean(mpg$cty)`.

* The average highway mpg is `r mean(mpg$hwy)`.

This report was generated on `r format(Sys.Date(), format = "%B %d, %Y")`.

About Report
========================================

Created by: BA-Data Analytics Class 2020

Confidential: HIGHLY!





